### 2018-03-18 Sections/mathematical_representation_of_quantum_networks.tex
Fusion gates fig. Stubs for fusion strategies
Fixed graphic sizes, added stubs for QEC, added quantum Stockmarket, minor tweaks
Latin quote stubs
minor

\subsection{Cost vector analysis} \label{sec:costs} \index{Cost vectors}\index{Attributes}

@@

\begin{definition}[Network cost metrics] \label{def:metric} Cost metrics satisfy the properties:\index{Network cost metrics}
	\begin{itemize}
    	\item Identity operations: If a channel performs nothing, its associated cost is zero, \mbox{$c(\mathbb{\hat{I}}) = 0$}.
    	\item Triangle inequality: \\ $c(v_1\to v_2\to v_3) \leq c(v_1\to v_2) + c(v_2\to v_3)$, \\ across all paths \mbox{$v_1 \to v_2 \to v_3$}. In the case of strict equality under addition we refer to the cost as a \emph{strictly additive cost}.
    	\item Positivity: \mbox{$c\geq 0$}. This ensures that shortest-path algorithms will function correctly. It is also congruent with the intuitive expectation that data traversing a communications channel is not somehow better off than if it hadn't traversed that channel at all.
	\end{itemize}
\end{definition}
Attributes, on the other hand do not have a distance interpretation, and may have arbitrary structure. A detailed discussion on the relationship between costs and attributes is presented in Sec.~\ref{sec:c_vs_a}.

@@

\begin{figure}[!htb]
\includegraphics[width=0.65\columnwidth]{example_routes}
\caption{Example of a simple network with multiple routes \mbox{$A\to B$}. Note that $R_3$ and $R_4$ are competing with one another for use of the last link, which the routing strategy, $\mathcal{S}$, will need to resolve if multiple simultaneous transmissions are taking place.} \label{fig:example_routes}
\end{figure}

\begin{figure}[!htb]
\includegraphics[width=0.6\columnwidth]{example_opt}
\caption{The same network graph from Fig.~\ref{fig:example_routes}, with links weighted by some arbitrary cost metric. Applying a shortest-path algorithm yields the optimal route between Alice and Bob to be \mbox{$A\to F\to B$}, which incurs a net cost of \mbox{$c=2$}, as opposed to all other routes, which incur a net cost of \mbox{$c=3$}.} \label{fig:simp_route_opt}
\end{figure}

>>>>

\subsection{Cost vector analysis} \label{sec:costs} \index{Cost vector analysis}\index{Attributes}

@@

\begin{definition}[Network cost metrics] \label{def:metric} Cost metrics satisfy the properties:\index{Network cost metrics}
	\begin{itemize}
    	\item Identity operations: If a channel performs nothing, its associated cost is zero, \mbox{$c(\mathbb{\hat{I}}) = 0$}.
    	\item Triangle inequality: \\ $c(v_1\to v_2\to v_3) \leq c(v_1\to v_2) + c(v_2\to v_3)$, \\ across all paths \mbox{$v_1 \to v_2 \to v_3$}. In the case of strict equality under addition we refer to the cost as a \textit{strictly additive cost}.
    	\item Positivity: \mbox{$c\geq 0$}. This ensures that shortest-path algorithms will function correctly. It is also congruent with the intuitive expectation that data traversing a communications channel is not somehow better off than if it hadn't traversed that channel at all.
	\end{itemize}
\end{definition}
Attributes, on the other hand do not have a distance interpretation, and may have arbitrary structure. A detailed discussion on the relationship between costs and attributes is presented in Sec.~\ref{sec:c_vs_a}.

@@

\begin{figure}[!htb]
\includegraphics[width=0.325\textwidth]{example_routes}
\caption{Example of a simple network with multiple routes \mbox{$A\to B$}. Note that $R_3$ and $R_4$ are competing with one another for use of the last link, which the routing strategy, $\mathcal{S}$, will need to resolve if multiple simultaneous transmissions are taking place.} \label{fig:example_routes}
\end{figure}

\begin{figure}[!htb]
\includegraphics[width=0.3\textwidth]{example_opt}
\caption{The same network graph from Fig.~\ref{fig:example_routes}, with links weighted by some arbitrary cost metric. Applying a shortest-path algorithm yields the optimal route between Alice and Bob to be \mbox{$A\to F\to B$}, which incurs a net cost of \mbox{$c=2$}, as opposed to all other routes, which incur a net cost of \mbox{$c=3$}.} \label{fig:simp_route_opt}
\end{figure}

### 2018-03-18 Sections/protocols_for_the_quantum_internet.tex
minor

There are four Bell states\footnote{$\ket{\Psi^-}$ is also referred to as a \emph{singlet} state, and $\ket{\Psi^+}$ as a \emph{triplet} state.}, defined as, 
\begin{align} \label{eq:bell_basis}
\ket{\Phi^{\pm}} &= \frac{1}{\sqrt{2}} (\ket{0}_A\ket{0}_B \pm \ket{1}_A\ket{1}_B), \nonumber \\
\ket{\Psi^{\pm}} &= \frac{1}{\sqrt{2}} (\ket{0}_A\ket{1}_B \pm \ket{1}_A\ket{0}_B),
\end{align}
which are locally equivalent to one another via the application of Pauli operators, and may therefore be transformed to one another without classical or quantum communication between the two parties. Specifically,
\begin{align}
\ket{\Phi^+} = \hat{Z}\ket{\Phi^-} = \hat{X}\ket{\Psi^+} = \hat{X}\hat{Z}\ket{\Psi^-},
\end{align}
where $\hat{X}$ and $\hat{Z}$ could apply to either qubit, up to global phase.

@@

@@

@@

\emph{Superdense coding} is a communications protocol, which utilises shared entanglement between two parties to increase the rate at which classical information may be transmitted between them.

>>>>

There are four Bell states\footnote{$\ket{\Psi^-}$ is also referred to as a \textit{singlet} state, and $\ket{\Psi^+}$ as a \textit{triplet} state.}, defined as, 
\begin{align} \label{eq:bell_basis}
\ket{\Phi^{\pm}} &= \frac{1}{\sqrt{2}} (\ket{0}_A\ket{0}_B \pm \ket{1}_A\ket{1}_B), \nonumber \\
\ket{\Psi^{\pm}} &= \frac{1}{\sqrt{2}} (\ket{0}_A\ket{1}_B \pm \ket{1}_A\ket{0}_B),
\end{align}
which are locally equivalent to one another via the application of Pauli operators, and may therefore be transformed to one another without classical or quantum communication between the two parties. Specifically,
\begin{align}
\ket{\Phi^+} = \hat{Z}\ket{\Phi^-} = \hat{X}\ket{\Psi^+} = \hat{X}\hat{Z}\ket{\Psi^-},
\end{align}
where $\hat{X}$ and $\hat{Z}$ could apply to either qubit, up to global phase.

@@

\comment{Include some equations}

@@

%
% Weak Measurement
%

\subsubsection{Weak measurement}

@@

\textit{Superdense coding} is a communications protocol, which utilises shared entanglement between two parties to increase the rate at which classical information may be transmitted between them.

### 2018-03-18 Sections/quality_of_service.tex
minor

Note that the protocol doesn't require that the $M$ instances of the unitary be held locally. They could be distributed, with the independent copies held by entirely different parties in distant locations.

>>>>

Note that the protocol doesn't require that the $M$ instances of the unitary be held locally. They operate independently in parallel and could therefore be distributed, with the independent copies held by entirely different parties in distant locations.\index{Distributed computation}\index{Parallelisation}
